---
title: "homework 5"
author: Purnima Sharma
date: "11/10/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(ggplot2)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,         
  out.width = "90%"      
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis", 
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

## Problem 1

To look at the proportion of unsolved homicides in 50 major U.S. cities.

Read data.

```{r}
homicide_df =
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

Analyzing data.

```{r}
aggregate_df =
  homicide_df %>% 
    group_by(city_state) %>% 
    summarize(
      hom_total = n(),
      hom_unsolved = sum(resolved == "unsolved")
   )
```

Trying Prop test for a single city (Baltimore).

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved),
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Using iteration to calculate for rest of the cities.

```{r}
results_df = 
  aggregate_df %>% 
    mutate(
      prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
      tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
    ) %>% 
    select(-prop_tests) %>% 
    unnest(tidy_tests) %>% 
    select(city_state, estimate, conf.low, conf.high)
```


Graphing resulting dataframe.

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


## Problem 2

### Longitudinal study analysis of 10 participants, with 8 weeks of observations.

Read data.

```{r}
path_df = 
  tibble(
    path = list.files("lda_data")
  ) %>% 
  mutate(
    path = str_c("lda_data/", path),
    data = map(.x = path, ~read_csv(.x))
    )
```

tidy the data.

```{r}
lda_df = 
   path_df %>% 
  mutate(path = str_replace(path, "\\lda_data/", "")) %>% 
  separate(path, into = c("arm", "id"), sep = "\\_") %>% 
  mutate(
    id = str_replace(id, "\\.csv", ""),
    arm = replace(arm, arm == "con", "control")
  ) %>% 
  select(id, everything()) %>% 
  unnest(data) %>% 
   pivot_longer(
     week_1:week_8,
     names_to = "week",
     names_prefix = "week_",
     values_to = "obs"
   )

lda_df
```

Spaghetti plot

```{r}
lda_df %>% 
    ggplot(
      aes(x = week, y = obs, color = arm, group = interaction(arm, id)),
      alpha = 0.3,) +
    geom_line() +
    ggtitle("Observations over time")
```

The graph indicates that on an average the values of observations were higher for subjects in the experimental group versus when in the control group. Also, the average trend in the experimental group showed increasing observation-values over the 8 weeks time period, versus more or less consistent values in the control arm.


## Problem 3

To explore power in a simple linear regression, using simulation.

Setting up the t-test function

```{r}
sim_mean_p = function(samp_size = 30, mu, sigma = 5) {
  
sim_data = 
  tibble(
      obs = rnorm(n = samp_size, mean = mu, sd = sigma)
  ) 

sim_result = 
  nest(sim_data) %>% 
  mutate(
  t_test = map(.x = data, ~t.test(x = .x, mu = 0, alternative = 'two.sided', paired = FALSE, conf.level = 0.95)),
  tidy_test = map(.x = t_test, ~broom::tidy(.x))
  ) 

return(sim_result)

}
```

Simulating data 5,000 times for each mean, using function

```{r}
simulation_results =   
  tibble(
    true_mean = c(0, 1, 2, 3, 4, 5, 6)
  ) %>% 
  mutate(
    output_lists = map(.x = true_mean, ~ rerun(50,sim_mean_p(mu = .x))),  
     estimate_df = map(output_lists, bind_rows)
  ) %>% 
  select(-output_lists) %>%
  unnest(estimate_df)  
  
simulation_results =
simulation_results %>% 
  unnest(tidy_test)

simulation_results =
 simulation_results %>%  
  mutate(
    mu_hat = estimate,
    p_value = p.value
  ) %>% 
  select(true_mean, mu_hat, p_value)

head(simulation_results)
```




